Is there a Criterion in Criterial Learning? \\ \vspace{.08in} Insights from Studying Feedback Delays

### 2025-10-17 write/response_to_reviews_GA.tex

\subsubsection{Author response}
We thank the reviewer for catching this confusion. No study
was deleted from the manuscript. Rather, whether or not the
computational modeling section should be considered an
``experiment'' was a point of oscillation when writing. This
comment, along with comment 3 of Reviewer 1 and comment 2 of
Reviewer 2 helped us see that referring to the modeling
section as Experiment 1 was a mistake. As explained in our
responses to both of those comments, the revision refers to
the two empirical experiments as Experiments 1 and 2. These
are now presented first, and then following by a modeling
section entitled ``New Computational Models of Criterial
Learning.''

\subsection{AE comment 9}
In figure 6, it is clear that the participants form two
subcohorts. However, the use of a Gaussian seems odd given
that there can not be any negative values for
trials-to-criterion. Given that the authors model this
frequency histogram to exclude participants, more
appropriate distributions, such as Poisson should be used.

\subsubsection{Author response}
This is a good point that is similar to comment 3 of
Reviewer 2. Rather than use a mixture model based on the
Poisson distribution, we took the advice of Reviewer 2 and
used the ExGaussian as our base distribution. Specifically,
as described in our response to comment 3 of Reviewer 2, we
now fit the trials-to-criterion data collapsed across
conditions and participants with both a single-component
truncated ExGaussian and a two-component truncated
ExGaussian mixture via MLE with proper normalization on the
tasks bounded support $[9,512]$.

\subsection{AE comment 10}
Given the experimental results, what is the added benefit of
the three models? Experiment 2 is the critical experiment
showing that 3.5-0.5 leads to more trials-to-criterion than
0.5-3.5 or 0.5-0.5. The models do not provide any detailed
understanding of mechanisms and they are not fitted to
actual data. The general message from the experiments is
that any updating rule should be sensitive to feedback
delay. The models do not go beyond this.

\subsubsection{Author response}
The experiments show that feedback delay impairs criterial
learning, but they do not speak to the question of
underlying mechanism. The modeling is critical to this
question. Specifically, the computational analysis attempts
to establish constraints on underlying mechanisms that are
compatible with the empirical results. We believe that PSP
is a better approach, given this goal, than the more
traditional approach of fitting the models to the observed
data. This is now explained in the following new paragraph
(paragraph 2 of the ``Simulation Results'' section):

``Our approach was to generate predictions for each of the
three experimental conditions across a wide range of
parameter values. We then used parameter-space partitioning
(PSP) to evaluate the performance of each model (Pitt et
al., 2006). Traditional computational modeling identifies
parameter values that allow the model to provide the best
possible fit to the observed data. This traditional approach
therefore treats the single observed data set being fit as a
gold standard. Our goal instead was to investigate the range
of possible predictions of each model. We were interested in
questions such as: can a model predict any possible outcome
or is it constrained to always predict, for example, that
feedback delays impair learning? PSP was designed to answer
such questions.''

Furthermore, we believe this PSP analysis produced some
surprising and important results. First, it showed that
SR-learning accounts are compatible with our results -- even
if they assume that the amount of synaptic updating that
occurs trial-by-trial is unaffected by feedback delay.
Second, the PSP analysis showed that, in contrast,
stored-criterion accounts of Experiments 1 and 2 must assume
that feedback delays impair the criterion-updating process
-- a result that greatly constrains the type of memory that
could be used to store and update the criterion. For
example, it rules out working memory because many previous
results show that working memory is immune to short 3 s
delays. We believe these inferences would be impossible
without our computational modeling approach. In this way,
the models contribute the most important piece: they pin
down the process-level mechanisms consistent with the
experiments.

\end{document}
